---
title: "Reality Mining Predictability EDA"
author: "Stephanie"
date: "4/16/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(install.load)
install_load('R.matlab')
install_load('plotly')
install_load('ggplot2')
install_load('lubridate')
#install_load('networkD3')
```

Subject 10 considers themselves very predictable. I'll work to implment two visualizations on this subject to determine if their schedule is truly predictable or not.

### Heatmap

```{r cars}
load(file = "data/s10data.Rda")
s10data <- as.data.frame(s10data)

colnames(s10data) <- c("Date", as.character(1:24))
rownames(s10data) <- c(seq(1:140))

start_date <- as.POSIXct((732200 - 719529)*86400, origin = "1970-01-01")
end_date <- as.POSIXct((732339.905636574 - 719529)*86400, origin = "1970-01-01")
```


```{r}
s10data$Date <- as.Date(s10data$Date, format = "%m/%d/%Y")
s10data$day <- weekdays(as.Date(s10data$Date))
```

I need a new data frame where the probabilities are calculated in the cells. 

```{r}
HOME <- '1'
WORK <- '2'
ELSEWHERE <- '3'
NO_SIGNAL <- '4'
PHONE_OFF <- NaN

#example of 24th hour probability for friday

days_of_week <- c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday")

total_friday <- sum(s10data$day == "Friday")

total_home_friday <- sum(s10data$day == "Friday" & s10data$'24'==HOME)

probability <- total_home_friday/total_friday

```

I should probably create a function to do these probabilities quickly and at once.. below I will work to create this function.

This function takes in the day of the week and the location we want to compute the probability for. 

```{r}
#function to get the probability of being home on a friday for each hour in a day 


func2 <- function(input_day) {
    vr <- c() ### an empty vector 

    for (i in 1:24) { 
      
        total_day <- sum(s10data$days == input_day)
        total_instance <- sum(s10data$days == input_day & s10data[,i+1]== '1')
        probability <- total_instance/total_day
        
        vr[i] <- probability
        
    }
    vr
}

func2("Friday")

```

```{r}


  
func3 <- function(input_day, location) {
    vr <- c() ### an empty vector 

    for (i in 1:24) { 
      
        total_day <- sum(s10data$days == input_day)
        total_instance <- sum(s10data$days == input_day & s10data[,i+1]== location)
        probability <- total_instance/total_day
        
        vr[i] <- probability
        
    }
    vr
}

func3("Friday","2")

```

```{r}

func4 <- function(input_day, location) {
    vr <- c() ### an empty vector 
    probability_skeleton <- data.frame()
    for (j in 1:length(input_day)){
        for (i in 1:24) { 
      
        total_day <- sum(s10data$day == input_day)
        total_instance <- sum(s10data$day == input_day & s10data[,i+1]== location)
        probability <- total_instance/total_day
        
        vr[i] <- probability
        
        }
        
        
    }
    vr
}

hold <-func4("Monday","2")

hold[3]
```

I'm going to create a data from for the probability that the person is 1-home 2-work 3-elsewhere, below is the example for the probability the subject is at home 

```{r}

d <- data.frame(matrix(nrow=24, ncol=7))

for (i in 1:length(days_of_week)){
  
  d[,i] <- cbind(func4(days_of_week[i], HOME))
  
}

colnames(d) <- days_of_week

heatmap_home <- heatmap(as.matrix(d), Rowv=NA, Colv=NA, col = cm.colors(256),scale="none", margins=c(5,10))

```

The subject is at work 

```{r}
d2 <- data.frame(matrix(nrow=24, ncol=7))

for (i in 1:length(days_of_week)){
  
  d2[,i] <- cbind(func4(days_of_week[i], WORK))
  
}

colnames(d2) <- days_of_week

heatmap_work <- heatmap(as.matrix(d2), Rowv=NA, Colv=NA, col = cm.colors(256),scale="none", margins=c(5,10))

```

The subject is else where 

```{r}
d3 <- data.frame(matrix(nrow=24, ncol=7))

for (i in 1:length(days_of_week)){
  
  d3[,i] <- cbind(func4(days_of_week[i], ELSEWHERE))
  
}

colnames(d3) <- days_of_week
heatmap_elsewhere <- heatmap(as.matrix(d3), Rowv=NA, Colv=NA, col = cm.colors(256),scale="none", margins=c(5,10))
```

Next I'm going to work on creating heatmaps for each place

```{r}

#p <- plot_ly(z=d3, type = "heatmap")
#p
#heatmap(d3)

#confidence band, variance 
#measure of standard error 
#(time series)
#narrative transition

```



How will these probability heatmaps look for someone who doesn't consider themselves predictable? 

```{r}

```

### Line graph

```{r}

#sn_startdate <- readMat("")


loc <- readMat("data/withdate.mat")
#1st column
val <- loc[["withdate"]][[1]][,1]
val <- as.POSIXct((val - 719529)*86400, origin = "1970-01-01")

#create data frame with date and location
date_location <- data.frame(val,loc[["withdate"]][[1]][,2])
colnames(date_location) <- c("date","location")
home <- 5119.40811000000
date_location$location[date_location$location == home] <- "Home"
#get day of the week in new column
date_location$days <- weekdays(as.Date(date_location$date))
date_location$time <- as.numeric(format(date_location$date,"%H"))
when_home <- dplyr::filter(date_location, date_location$location == "Home")
a <- ggplot(when_home, aes(days,time)) + geom_point(alpha=.2) + scale_x_discrete(limits=c("Sunday","Monday","Tuesday","Wednesday","Thursday", "Friday","Saturday"))
a

#start w/ values of hour greater than 8
when_home8 <- dplyr::filter(when_home, when_home$time > 8)
b <- ggplot(when_home8, aes(days,time)) + geom_point(alpha=0.5) + scale_x_discrete(limits=c("Sunday","Monday","Tuesday","Wednesday","Thursday", "Friday","Saturday"))
b

```

```{r}
#loc2 <- readMat("data/places.mat")
```
My next task is to create a line graph, where each line represents the time the subject went home after being logged at work for a particular week. 
I'm going to use s10data to create this new data frame and create a new column that groups days into weeks. 

```{r}

dates_week <- s10data %>% 
  mutate(week = cut.Date(Date, breaks = "1 week", labels = FALSE, start.on.monday = FALSE)) %>% 
  arrange(Date)

```

Now that I have a column that groups days into weeks, I need to work to create a new data structure with the kind of line graph I want. 


```{r}

test <- dates_week %>% filter(dates_week[,2:26] == 1)

dates_week[,2:26]

#loop that goes through column to find 1st instance where 2 is followed by a 1 (went from work to home)

store <- as.numeric(dates_week[1,2])


```

```{r}

home_from_work <- data.frame(matrix(nrow=140, ncol=2))


for (i in range(1:nrow(s10data))){
  for (m in range(2:25)){
    location = as.numeric(dates_week[i,m])
    if (location == 2){
      for (n in range(m+1:25)){
        check = as.numeric(dates_week[i,n])
        if(check == 1){
          hour = n
          dates = dates_week[i,1]
          home_from_work[i,1] <- dates
          home_from_work[i,2] <- hour
          break
        }
      }
      
    }
    #add hour and date to dataframe
    
    
  }
  
  
}


```



```{r}

df3 <- data.frame(matrix(nrow=1, ncol=2))

dates_week <- as.matrix(dates_week)


  for (m in range(2:25)){
    location = as.numeric(dates_week[1,m])
    
    if (location == 2){
      for (n in range(m+1:25)){
        check = as.numeric(dates_week[1,n])
        print(n)
          if(check == 1){
            hour = colnames(dates_week)[n]
          
            dates = dates_week[1,1]
            df3[1,1] <- dates
            df3[1,2] <- hour
            break
        }
       
      }
      #break here prints location once
      break
    }
  }
```

```{r}


df2 <- data.frame(matrix(nrow=1, ncol=2))

dates_week <- as.matrix(dates_week)

  for (m in 2:25){
    location = as.numeric(dates_week[1,m])
    if (location == 2){
      for (n in m+1:25){
        check = as.numeric(dates_week[1,n])
        if(check == 1){
          hour = colnames(dates_week)[n]
          dates = dates_week[1,1]
          df2[1,1] <- dates
          df2[1,2] <- hour
        break
        }
        
      }
      break
    }
    #add hour and date to dataframe
    
    
  }

```



```{r}
df5 <- data.frame(matrix(nrow=1, ncol=2))

dates_week <- as.matrix(dates_week)

  for (m in 2:25){
    location = as.numeric(dates_week[1,m])
    if(is.na(location)){
       
      }
    if (location == 2){
      for (n in m+1:25){
        check = as.numeric(dates_week[1,n])
        if (is.na(check)){
          break
        }
        if(check == 1){
          hour = colnames(dates_week)[n]
          dates = dates_week[1,1]
          df5[1,1] <- dates
          df5[1,2] <- hour
        break
        }
        
        
      }
      #this break is important
      break
    }
    
  }
```


this one works 

```{r}
df6 <- data.frame(matrix(nrow=nrow(s10data), ncol=2))

dates_week <- as.matrix(dates_week)

for (i in 1:nrow(s10data)){
  for (m in 2:25){
    location = as.numeric(dates_week[i,m])
    if(is.na(location)){
       break
      }
    if (location == 2){
      for (n in m+1:25){
        check = as.numeric(dates_week[i,n])
        if (is.na(check)){
          break
        }
        if(check == 1){
          hour = colnames(dates_week)[n]
          dates = dates_week[i,1]
          df6[i,1] <- dates
          df6[i,2] <- hour
        break
        }
        
        
      }
      #this break is important
      break
    }
    
  }
}

```

